A forest is more than its trees: haplotypes and inferred ARGs

### 2024-08-20 paper/writeup.tex
new title

\title{
    Information in recombination junctions 
    can both compress and improve inferred tree sequences
}

% Non-coalescing regions of dark matter in ARGs
% Can we find them? Are they useful in inference, dating? 
% Look, we can find them and they seem at least useful for compression.
% Also, here's a way of measuring agreement that takes this sort of thing into account,
%  which extends R-F to measure haplotypes

@@

\begin{figure}[!ht]
	\begin{center}
\includegraphics[height=1.5in, width=3in]{discrepancy_func_method_t1.pdf}
\includegraphics[height=1.5in, width=3in]{discrepancy_function_method_t2.pdf}
    \caption{
        For two tree sequences $T1$ and $T2$ the \textit{discrepancy function}, $d(T1,T2)$, matches nodes in $T1$ with nodes in $T2$
        based on identical sample sets. We then measure each pair of nodes' \textit{shared span} across the entire tree sequence.
        In this example we have nodes $0$ through $7$ in $T1$ match with their identical counterpart. 
        Node $8$ has no match in $T2$ as there are no nodes in $T2$ with sample set $\left{1,2,3\right}$.
        \comment{make some reference to Discrepancy function section or appendix for more in depth calculation.}
        \label{fig:conceptual_discrepancy}
    }
	\end{center}
\end{figure}

>>>>

\title{
    A forest is more than its trees:
    haplotypes and inferred ARGs
}

% Information in recombination junctions can both compress and improve inferred tree sequences
% Non-coalescing regions of dark matter in ARGs
% Can we find them? Are they useful in inference, dating? 
% Look, we can find them and they seem at least useful for compression.
% Also, here's a way of measuring agreement that takes this sort of thing into account,
%  which extends R-F to measure haplotypes

@@

\begin{figure}[!ht]
	\begin{center}
\includegraphics[height=1.5in, width=3in]{discrepancy_func_method_t1.pdf}
\includegraphics[height=1.5in, width=3in]{discrepancy_function_method_t2.pdf}
    \caption{
        For two tree sequences $T1$ and $T2$ the \textit{discrepancy function}, $d(T1,T2)$, matches nodes in $T1$ with nodes in $T2$
        based on identical sample sets. We then measure each pair of nodes' \textit{shared span} across the entire tree sequence.
        In this example we have nodes $0$ through $7$ in $T1$ match with their identical counterpart. 
        Node $8$ has no match in $T2$ as there are no nodes in $T2$ with sample set $\left\{1,2,3\right\}$.
        \comment{make some reference to Discrepancy function section or appendix for more in depth calculation.}
        \label{fig:conceptual_discrepancy}
    }
	\end{center}
\end{figure}
